---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PITO2

<!-- badges: start -->
<!-- badges: end -->
<p align="center">
<img align="right" width="200" height="200" src="./logo.svg">
</p>

This is a satire statistical R package based on the counting-out rhyme "Pito pito gorgorito"
(https://es.wikipedia.org/wiki/Pito%2C_pito%2C_gorgorito), which has countless adaptations in
all languages and is used when a random choice is to be made.

The PITO2 package performs a **data independent variable selection** (DIVS, see also [this test](https://rdrr.io/cran/TeachingDemos/man/cortest.html)), based purely on random chance.

## Installation

You definitely shouldn't install nor use this package, but if you choose to, do this:

```{r eval=FALSE}
devtools::install_github("RogerGinBer/PITO2")
```

## Example

This is a basic example which shows you how to (incorrectly) solve a common problem:

```{r example}
library(PITO2)
metabolites <- paste("Metabolite", 1:100)
pitopito(metabolites, fdr = 0.05) #5% chance that any given metabolite is selected
```


